Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-05 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
GD mention of activity x location Appendix, flesh out

We also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. 
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children. Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. Each of these positions offer the child differing degrees of visual access to faces and hands. While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

>>>>

We also found an unexpectedly high proportion of hands in infants' view, even when restricting the analysis to detections in the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. 
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). 
Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. 
Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Appendix, Figure S7?) and between individual children. 
Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. 
This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. 
Each of these positions offer the child differing degrees of visual access to faces and hands. 
While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.
